---
title: "Iteration and Listcols"
author: "Yifan Su"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
set.seed(1)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Lists

You can put anything in a list.

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l

l$vec_numeric
l[[1]] # list the first element in the list
mean(l[["vec_numeric"]])
```

# `for` loops

Creat a new list.

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```


```{r}
# define the mean_and_sd() function
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}


```

I can apply that function to each list element.

```{r}
mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

Let's use a for loop:

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}
```

## Let's try map

```{r}
output = map(list_norms, mean_and_sd) # give input and the function, see if there is output, instead of using loop
output = map(.x = list_norms, ~ mean_and_sd(.x))
```

what if you want a different function..?

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = median(list_norms[[i]])
}
# similarly
output = map(list_norms, median) # output = map(.x = list_norms, ~ median(.x))
```

## `map` variants

```{r}
output = map_dbl(list_norms, median, .id = "input") # make it a double, like a tibble

output = map_df(list_norms, mean_and_sd, .id = "input") # keep track of id, put them into a column,  the output-specific map_dfr: this will produce a single data frame.

# output = map2(.x = input_1, .y = input_2, ~func(arg_1 = .x, arg_2 = .y)), variant map2 (and map2_dbl, etc) is helpful when your function has two arguments
```


## List columns and operations!

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    samp = list_norms
  )
```

```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)
listcol_df$samp[[1]]
```

Let's try some operations.

```{r}
mean_and_sd(listcol_df$samp[[1]])

# or I can just map? get the same mean and sd
map(listcol_df$samp, mean_and_sd)
```


```{r}
listcol_df = # add a summary column by map
  listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd),
         medians = map_dbl(samp, median)) # make it a double charactor.

listcol_df
```

## Nested data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Get our list columns...

```{r}
weather_nest = 
  nest(weather_df, data = date:tmin)

weather_nest

weather_nest %>% pull(name)
weather_nest %>% pull(data)
weather_nest$data[[1]] # 1-3 corresponding to three names
```

```{r}
unnest(weather_nest, cols = data)
```

Suppose i want to regress `tmax` on `tmin` for each station.

This works...

```{r}
lm(tmax ~ tmin, data = weather_nest$data[[1]])
```

Let's writer a function to do the regression.

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest$data[[1]])

output = vector("list", 3)

for (i in 1:3) {
  output[[i]] = weather_lm(weather_nest$data[[i]])
}
```

What about a map ..?

```{r}
map(weather_nest$data, weather_lm)
#similarly
map(weather_nest$data, ~lm(tmax ~ tmin, data = .x))
```

What about a map in a list column !!!!??

```{r}
weather_nest = 
  weather_nest %>% 
  mutate(models = map(data, weather_lm))

weather_nest
```

## Revisiting Napoleon

```{r}
read_page_reviews = function(url) {
  
  html = read_html(url)
  
  title = 
    html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = 
    html %>%
    html_nodes(".review-data:nth-child(5)") %>%
    html_text()
  
  tibble(title, stars, text)
}

url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

```{r}
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

dynamite_reviews = map_df(vec_urls, read_page_reviews)

dynamite_reviews = 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest()
```

