---
title: "Writing functions"
author: "Yifan Su"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
set.seed(1)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Do something simple

```{r}
x_vec = rnorm(25, mean = 5, sd = 3)

(x_vec - mean(x_vec)) / sd(x_vec)
```

I want a function to compute z-scores
```{r}
z_scores = function(x) {
  
  z = (x - mean(x)) / sd(x)
  return(z)
  
}

z_scores(x_vec) # the input is the x_vec
```

Try my function on some other things， this should give errors.

```{r error=TRUE}
z_scores = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Z scores cannot be computed for length 1 vectors")
  }
  
  z = mean(x) / sd(x)
  
  z
}

z_scores(3) # it shows NA
z_scores("my name is jeff")
z_scores(mtcars)
z_scores(iris)
z_scores(sample(c(TRUE, FALSE), 25, replace = TRUE))
```

## Multiple outputs

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
# or we can use list() function
  tibble(mean = mean_x, # we want to give both mean and sd, hope it returns both
       sd = sd_x)
}
```

Check tha the function works:

```{r}
mean_and_sd(x_vec)
```


## Multiple intputs

I'd like to do this a function.
```{r}
sim_data = 
  tibble(
  x = rnorm(30, mean = 2, sd = 3)
)

sim_data %>% 
  summarize(
    mu_hat = mean(x),
    sigma_hat = sd(x)
  )
```


```{r}

sim_mean_sd = function(sample_size, mu, sigma = 6) { # you can set a defult
  
  sim_data = 
    tibble(
    x = rnorm(n = sample_size, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}

sim_mean_sd(100, 6, 3) # numbers matches names # this overwrite the function
sim_mean_sd(100, 6)
```



url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}

url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews



